Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
RQ2 finished

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
     Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty
statements, since it is one of the main issues of dynamic slicing techniques. This
is particularly important because when \ds{} misses a faulty statement
means that it will not be in the diagnostic report and therefore has a negative
impact in the fault localization accuracy. Table~\ref{table:fsws} presents the
number of faults where at least one of the faulty statements appears in the
final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault,
we only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
of the highest faulty classes.

In~\ref{table:fsws}, we observe that

\combpar{k}
finds the faulty statements faster than \sfl{}$^{k}$. For both $k$ scenarios ($k=5$ or $k=10$), \combpar{k} performs better, i.e., it misses less faulty statements than \sfl{}$^{k}$.

\combpar{k}The best scena $23$ of the $260$ ($8.8\%$) faults do not include the
faulty statements in the slicer report after slicing the $10$ highest faulty classes.

Using \combpar{10} we are able to find more $20$ faulty
statements than when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$
of the faulty statements whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty
statements. Thus, \combpar{10} misses less $5.2\%$ of the faults against
\sfl{}$^{10}$.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{}
to improve fault localization. Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying the both
techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. We observe that
$33$ of the $260$
faulty versions do not include the faulty statements in the slicer report after slicing.
Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases where the faulty
statements where removed using \combpar{k}. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
Instead, if $K=10$ is considered the proposed approach returns an improvement of
$11.1$ on the rank mean of faulty statements.
 Figure \ref{fig:diagnosis} reports the performance of the diagnosis
using \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$,
respectively. Although this dataset has more than 50\% of fault of omissions,
our simple slicing approach was capable of improving the ranking of $97$ for
$k=5$ and $117$ for $K=117$ faults. Table \ref{table:st} presents the statistics
to determine if the observed results are statistically significant. Shapiro-Wilk
tests the null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With 99\% of confidence,
the results tell us that the distributions are not normal. Given that $C$ is not
normally distributed, we use the non-parametrical statistical hypothesis test,
Friedman. The null-hypothesis is that the ranking results of all techniques and
variants are the same. With 99\% of confidence, the results show that the
distributions are distinct. To understand if there is any relationship
between the distributions,
we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all the
distributions. With 99\% of confidence, it is possible to see that in general
the distributions are very similar. \Rui{so??}

>>>>

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]

  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
     Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}

@@

In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
statements, since it is one of the main issues of dynamic slicing techniques. This
is particularly important because when \ds{} misses a faulty statement
means that it will not be in the diagnostic report and therefore has a negative
impact in the fault localization accuracy. Table~\ref{table:fsws} presents the
number of faults where at least one of the faulty statements appears in the
final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault,
we only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
of the highest faulty classes.

In Table~\ref{table:fsws}, we observe that for both scenarios ($k=5$ and $k=10$), \combpar{k}
finds the faulty statements faster than \sfl{}$^{k}$. 
\sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas \combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e., 
\combpar{5} misses less $20$ ($7.7\%$) faults than \sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults where as \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10} misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$. There is also a significant difference within each technique. Generally, the majority of faulty statements are found on the $5$ highest ranked faulty classes. There are few cases where the faulty statements are only find if the approach considers the first $10$ highest ranked faulty classes. \combpar{10} is the variant of our approach
that performs better \textbf{missing only 23 out of 260 (8.8\%) cases}.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{}
to improve fault localization. Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$.

Figure
$33$ of the $260$
faulty versions represent cases where we find 
Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases where the faulty
statements where removed using \combpar{k}. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
Instead, if $K=10$ is considered the proposed approach returns an improvement of
$11.1$ on the rank mean of faulty statements.
 Figure \ref{fig:diagnosis} reports the performance of the diagnosis
using \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$,
respectively. Although this dataset has more than 50\% of fault of omissions,
our simple slicing approach was capable of improving the ranking of $97$ for
$k=5$ and $117$ for $K=117$ faults. Table \ref{table:st} presents the statistics
to determine if the observed results are statistically significant. Shapiro-Wilk
tests the null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With 99\% of confidence,
the results tell us that the distributions are not normal. Given that $C$ is not
normally distributed, we use the non-parametrical statistical hypothesis test,
Friedman. The null-hypothesis is that the ranking results of all techniques and
variants are the same. With 99\% of confidence, the results show that the
distributions are distinct. To understand if there is any relationship
between the distributions,
we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all the
distributions. With 99\% of confidence, it is possible to see that in general
the distributions are very similar. \Rui{so??}
